Figures

### 2019-05-16 figures/09_stream_buffer.Rmd
label focal lakes

```{r 09_stream_buffer, echo=FALSE, fig.height=3, fig.width=4}
dt <- readRDS("../data/dt.rds") %>%
  mutate(diff = stream_cultivated_crops - ag_pct, 
         category = cut(diff, breaks = c(Inf, 3, -65, -Inf))) %>%
  drop_na(diff)

ggplot(data = dt) +
  geom_point(aes(x = ag_pct, y = stream_cultivated_crops, color = category)) +
  geom_abline(aes(slope = 1, intercept = 3)) +
  geom_abline(aes(slope = 1, intercept = -65)) +
  theme(legend.position = 0) +
  ylab("Stream buffer Ag (%)") + xlab("IWS Ag (%)") +
  xlim(c(40, 100)) + ylim(c(0, 100))
```

```{r satellite, echo=FALSE}
# 
# res_pnt  <- query_gis("LAGOS_NE_All_Lakes_4ha_POINTS", "lagoslakeid", 
#                       dplyr::filter(dt, diff > 0)$lagoslakeid)
res_iws  <- query_gis("IWS", "lagoslakeid", 
                      dplyr::filter(dt, diff > 3)$lagoslakeid)

# ggplot() + 
#   geom_sf(data = state_sf()) +
#   geom_sf(data = res_pnt)

library(curl)
library(glue)
library(slippymath)
library(raster)
library(rgdal)

@@

outpaths     <- paste0("../data/mapbox/", res_iws$lagoslakeid, ".tif")
images       <- lapply(seq_along(outpaths), function(i) 
  get_if_not_exists(get_image, outpaths[i], raster::brick, iws = res_iws[i,]))

iws_sized    <- which(abs(res_iws$IWSAreaHa - median(res_iws$IWSAreaHa)) < 1000)
images_sized <- images[iws_sized]

get_streams <- function(destfile){
  res <- lapply(iws_sized, function(x) 
            nhdR::nhd_plus_query(
              poly = res_iws[x,], dsn = "NHDFlowLine")$sp$NHDFlowLine)
  saveRDS(res, destfile)
  return(res)
}

res_streams <- get_if_not_exists(get_streams, "../data/nhd/res_streams.rds")

# m <- viewRGB(r) + 
#   mapview(res_streams[[1]]) + 
#   mapview(s, alpha.regions = 0, color = "red")
# 
# mapshot(m, file = paste0(getwd(), "/map.png"))
# extent(r); st_bbox(s)

i          <- 7
s          <- res_iws[iws_sized[i],]
r_raw      <- images_sized[[i]]
r          <- projectRaster(r_raw, crs = as.character(st_crs(s))[2])

tab        <- as.data.frame(r, xy = TRUE)
names(tab) <- c("x", "y", "red", "green", "blue")
tab$red   <- scales::rescale(tab$red, to = c(0, 255))
tab$blue  <- scales::rescale(tab$blue, to = c(0, 255))
tab$green <- scales::rescale(tab$green, to = c(0, 255))
tab          <- tab[complete.cases(tab),]
tab$hex      <- rgb(tab$red, tab$green, tab$blue, maxColorValue = 255)

ggplot() + 
  geom_raster(data = tab, aes(x, y, fill = I(hex))) +
  geom_sf(data = res_iws[iws_sized[i],], alpha = 0, color = "red") +
  geom_sf(data = res_streams[[i]], color = "cyan") +
  coord_sf(datum = NA) +
  theme_void()

outpaths     <- paste0("../data/mapbox/", 6201, ".tif") # good sized but low stream ag
iws_temp     <- query_gis("IWS", "lagoslakeid", 6201)
# unlink("../data/mapbox/6201.tif")
images       <- lapply(seq_along(outpaths), function(i) 
  get_if_not_exists(get_image, outpaths[i], raster::brick, iws = iws_temp))

get_streams <- function(destfile){
  res <- lapply(iws_sized, function(x) 
            nhdR::nhd_plus_query(
              poly = iws_temp, dsn = "NHDFlowLine")$sp$NHDFlowLine)
  saveRDS(res, destfile)
  return(res)
}

streams_temp <- get_if_not_exists(get_streams, "../data/nhd/temp_streams.rds")
r_raw      <- images[[1]]
r          <- projectRaster(r_raw, crs = as.character(st_crs(s))[2])

tab        <- as.data.frame(r, xy = TRUE)
names(tab) <- c("x", "y", "red", "green", "blue")
tab$red   <- scales::rescale(tab$red, to = c(0, 255))
tab$blue  <- scales::rescale(tab$blue, to = c(0, 255))
tab$green <- scales::rescale(tab$green, to = c(0, 255))
tab          <- tab[complete.cases(tab),]
tab$hex      <- rgb(tab$red, tab$green, tab$blue, maxColorValue = 255)

ggplot() + 
  geom_raster(data = tab, aes(x, y, fill = I(hex))) +
  geom_sf(data = iws_temp, alpha = 0, color = "red") +
  geom_sf(data = streams_temp[[1]], color = "cyan") +
  coord_sf(datum = NA) +
  theme_void()
```

>>>>

```{r 09_stream_buffer, echo=FALSE, fig.height=3, fig.width=4}
dt <- readRDS("../data/dt.rds") %>%
  mutate(diff = stream_cultivated_crops - ag_pct, 
         category = cut(diff, breaks = c(Inf, 3, -65, -Inf))) %>%
  drop_na(diff) %>%
  dplyr::select(lagoslakeid, ag_pct, stream_cultivated_crops, 
                diff, category)

# llid 6201 as a low stream ag
# llid 7026 as a high stream ag
llids <- c("6201", "7026")

ggplot(data = dt) +
  geom_point(aes(x = ag_pct, y = stream_cultivated_crops, color = category)) +
  geom_abline(aes(slope = 1, intercept = 3)) +
  geom_abline(aes(slope = 1, intercept = -65)) +
  ggrepel::geom_text_repel(data = dplyr::filter(dt, lagoslakeid %in% llids), 
            aes(x = ag_pct, y = stream_cultivated_crops, label = lagoslakeid)) + 
  theme(legend.position = 0) +
  ylab("Stream buffer Ag (%)") + xlab("IWS Ag (%)") +
  xlim(c(40, 100)) + ylim(c(0, 100))
```

```{r satellite, echo=FALSE}
# res_pnt  <- query_gis("LAGOS_NE_All_Lakes_4ha_POINTS", "lagoslakeid", 
#                       dplyr::filter(dt, diff > 0)$lagoslakeid)
# ggplot() + 
#   geom_sf(data = state_sf()) +
#   geom_sf(data = res_pnt)

library(curl)
library(glue)
library(slippymath)
library(rgdal)

res_iws  <- query_gis("IWS", "lagoslakeid", llids)

@@

outpaths     <- paste0("../data/mapbox/", llids, ".tif")
images       <- lapply(seq_along(outpaths), function(i) 
  get_if_not_exists(get_image, outpaths[i], raster::brick, iws = res_iws[i,]))

get_streams <- function(destfile){
  res <- lapply(seq_along(llids), function(x) 
            nhdR::nhd_plus_query(
              poly = res_iws[x,], dsn = "NHDFlowLine")$sp$NHDFlowLine)
  saveRDS(res, destfile)
  return(res)
}

# unlink("../data/nhd/res_streams.rds")
res_streams <- get_if_not_exists(get_streams, "../data/nhd/res_streams.rds")

prep_ggplot_raster <- function(r, iws){
  r_raw <- r
  r     <- projectRaster(r_raw, 
                         crs = as.character(st_crs(iws))[2])
  tab        <- as.data.frame(r, xy = TRUE)
  names(tab) <- c("x", "y", "red", "green", "blue")
  tab$red   <- scales::rescale(tab$red, to = c(0, 255))
  tab$blue  <- scales::rescale(tab$blue, to = c(0, 255))
  tab$green <- scales::rescale(tab$green, to = c(0, 255))
  tab          <- tab[complete.cases(tab),]
  tab$hex      <- rgb(tab$red, tab$green, tab$blue, maxColorValue = 255)
  tab
}

i <- 1
gg_low_ag <- ggplot() + 
  geom_raster(data = prep_ggplot_raster(images[[i]], res_iws[i,]), 
              aes(x, y, fill = I(hex))) +
  geom_sf(data = res_iws[i,], alpha = 0, color = "red") +
  geom_sf(data = res_streams[[i]], color = "cyan") +
  coord_sf(datum = NA) +
  theme_void() +
  ggtitle(llids[i])

i <- 2
gg_hi_ag <- ggplot() + 
  geom_raster(data = prep_ggplot_raster(images[[i]], res_iws[i,]), 
              aes(x, y, fill = I(hex))) +
  geom_sf(data = res_iws[i,], alpha = 0, color = "red") +
  geom_sf(data = res_streams[[i]], color = "cyan") +
  coord_sf(datum = NA) +
  theme_void() +
  ggtitle(llids[i])

cowplot::plot_grid(gg_low_ag, gg_hi_ag)
```

### 2019-05-16 manuscript/figures.Rmd
label focal lakes

```{r big_stream_ag, fig.cap = "Stream buffer Ag >> IWS", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/satellite-1.pdf")
```

```{r small_stream_ag, fig.cap = "Stream buffer Ag << IWS", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/satellite-2.pdf")
```

>>>>

```{r big_stream_ag, fig.cap = "Stream buffer Ag compared to IWS Ag.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/satellite-1.pdf")
```
